---
title: "Prior-Posterior Comparisons and Correlation Checks"
author: "Catherine Bradley"
date: '`r format(Sys.time(), "%d %B, %Y")`'
output: pdf_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, message = FALSE, warning = FALSE}
library(jagsUI)
library(PerformanceAnalytics)
```

```{r, include = FALSE}
out <- readRDS("IPM_forPriorPostComp.rds") # using lead constant, RCP4.5
str(out$sims.list)
post <- out$sims.list #posterior samples

# transparent colors for prior (pri) and posterior (post)
pri.col <- rgb(0, 0, 255, max = 255, alpha = 100, names = "blue50")
post.col <- rgb(255, 0, 0, max = 255, alpha = 100, names = "red50")

# subset from the posteriors
set.seed(85)
hold <- sample(c(1:40000), 2000, replace = FALSE)
```
All results here are based on the model used in the SSA in Fall 2020, under scenario RCP4.5/Constant Lead.
```{r, echo = TRUE, eval = FALSE, warning = FALSE, message = FALSE}
# parameters monitored
parameters <- c("mean.logit.phi0", "mean.phiA", "betaN", 
                "beta", "mean.log.F", "sigma.phiA", "sigma.phi0", "sigma.d", "sigma.o",
                "mean.logit.BP", "betaF.ice", "betaF.ice2", "phiA", "phi0", "F", "BP")
# MCMC settings
ni <- 30000; nt <- 1; nb <- 20000; nc <- 4
```



In the following figures, prior distribution is blue, posterior distribution is red.
Median values for each are indicated by vertical lines in their respective colors.

# mean.phi0
## prior mean.phi0 = beta(15,45)
```{r}
prior <- rbeta(2000, 15, 45)
poster <- plogis(post$mean.logit.phi0[hold])

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topright", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# mean.phiA
## prior beta(90,10)
```{r}
prior <- rbeta(2000, 90, 10)
poster <- post$mean.phiA[hold]

b <- (min(c(prior,poster)) - 0.01)*100
e <- (max(c(prior,poster)) + 0.01)*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

\newpage
# betaN[1] fecundity
## prior 1/exp(norm(7.95, 3.31))
**NOTE**: The n.eff for this parameter and betaN[2] is 1, R-hat below 1.02 for both.
(n.eff is > 300 for all other monitored parameters)

```{r}
prior <- 1/exp(rnorm(2000, 7.95, sqrt(1/3.31)))
poster <- post$betaN[hold,1]

b <- min(c(prior,poster))*100000 - 0.001
e <- max(c(prior,poster))*100000
breaks <- (pretty(b:e, n = 20, min.n = 20))/100000

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topright", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# betaN[2] survival
## prior 1/exp(norm(7.95, 3.31))
```{r}
prior <- 1/exp(rnorm(2000, 7.95, sqrt(1/3.31)))
poster <- post$betaN[hold,2]

b <- min(c(prior,poster))*100000 - 0.001
e <- max(c(prior,poster))*100000
breaks <- (pretty(b:e, n = 20, min.n = 20))/100000

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topright", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

Given the n.eff for these two parameters, is there non-identifiability between them?

```{r}
betaN1 <- post$betaN[hold,1]
betaN2 <- post$betaN[hold,2]

plot(betaN1~ betaN2)
```

Not really at all...What do the traceplots look like?

```{r}
traceplot(out, parameters = "betaN")
```
Traceplots look fine as well. https://github.com/kenkellner/jagsUI/issues/17: looks like it is a consequence of the calculation of n.eff when the absolute value of the parameter is small. Option is to standardize input (in this case count) to adjust, but it doesn't appear to be any problem with convergence/estimation with these.


# beta[1] ice effect on phi.A
## prior norm(0,100)
```{r}
prior <- rnorm(2000, 0, 0.1)
poster <- post$beta[hold,1]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# beta[2] ice^2 effect on phi.A
## prior norm(0,100)
```{r}
prior <- rnorm(2000, 0, 0.1)
poster <- post$beta[hold,2]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

this is counter to what EO found in exploring GAMS for these functions using the 
CMR data only. Look at mean phiA ~ ice.

```{r}
ext.sea.ice <- read.csv("input_data/extreme.sea.ice.csv", header = T)
# year is winter year (Nov - Apr)
ice.data <- ext.sea.ice[ext.sea.ice$year >= 1988 & ext.sea.ice$year <= 2100,]
ice.data4.5 <- ifelse(is.na(ice.data$ice.obs), ice.data$ice.RCP4.5, 
                      ice.data$ice.obs)
yearly.phiA <- apply(post$phiA,2,mean) # eider year 1993 - 2015

plot(yearly.phiA[5:27] ~ ice.data$ice.obs[6:28])
plot(yearly.phiA ~ ice.data4.5[2:113])

```

Over the observed period, it's exactly the same as obtained in the CJS-only model.

# beta[3] ice effect on phi.0
## prior norm(0,100)
```{r}
prior <- rnorm(2000, 0, 0.1)
poster <- post$beta[hold,3]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

\newpage
# beta[4] ice^2 effect on phi.0
## prior norm(0,100)
**NOTE**: Much stronger evidence for a quadratic effect of ice on juve survival than on
adult survival. f = 0.814 for beta[4], 0.568 for beta[2]

```{r}
prior <- rnorm(2000, 0, 0.1)
poster <- post$beta[hold,4]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# mean.log.F
## prior norm(-0.47,100)
```{r}
prior <- rnorm(2000, -0.47, 0.1)
poster <- post$mean.log.F[hold]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# sigma.phiA
## prior unif(0,1)
**NOTE**: We talked about changing these to gammas at some point to avoid the truncation. Final thoughts?
```{r}
prior <- runif(2000, 0, 1)
poster <- post$sigma.phiA[hold]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# sigma.phi0
## prior unif(0,1)
```{r}
prior <- runif(2000, 0, 1)
poster <- post$sigma.phi0[hold]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# sigma.d
## prior gamma(2,13)
```{r}
prior <- rgamma(2000, 2, 13)
poster <- post$sigma.d[hold]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topright", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# sigma.o
## prior gamma(1,10)
```{r}
prior <- rgamma(2000, 1, 10)
poster <- post$sigma.o[hold]

b <- min(c(prior,poster))*100 - 0.001
e <- max(c(prior,poster))*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topright", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# mean.logit.BP
## prior norm(0.472, 0.22) T(-0.77, 3.22)
**NOTE**: This one and the next two priors should change with additional information
from the experts.
```{r}
prior <- rnorm(10000, 0.472, sqrt(1/0.22))
prior <- ifelse(prior < -0.77 | prior > 3.22, NA, prior)
prior <- prior[is.na(prior) == FALSE]
prior <- sample(prior, 2000, replace = FALSE)
poster <- post$mean.logit.BP[hold]

b <- min(c(prior,poster), na.rm = TRUE)*100 - 0.001
e <- max(c(prior,poster), na.rm = TRUE)*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster, na.rm = TRUE), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster, na.rm = TRUE), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# betaF.ice
## prior norm(2.83, 0.11) T(-1, 3)
```{r}
prior <- rnorm(10000, 2.83, sqrt(1/0.11))
prior <- ifelse(prior < -1 | prior > 3, NA, prior)
prior <- prior[is.na(prior) == FALSE]
prior <- sample(prior, 2000, replace = FALSE)
poster <- post$betaF.ice[hold]

b <- min(c(prior,poster), na.rm = TRUE)*100 - 0.001
e <- max(c(prior,poster), na.rm = TRUE)*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster, na.rm = TRUE), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster, na.rm = TRUE), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```

# betaF.ice2
## prior dnorm(-1.17, 0.69) T(-1.21, 0.33)
```{r}
prior <- rnorm(10000, -1.17, sqrt(1/0.69))
prior <- ifelse(prior < -1.21 | prior > 0.33, NA, prior)
prior <- prior[is.na(prior) == FALSE]
prior <- sample(prior, 2000, replace = FALSE)
poster <- post$betaF.ice2[hold]

b <- min(c(prior,poster), na.rm = TRUE)*100 - 0.001
e <- max(c(prior,poster), na.rm = TRUE)*100
breaks <- (pretty(b:e, n = 20, min.n = 20))/100

h.prior <- hist(prior, breaks = breaks, plot = FALSE)
h.poster <- hist(poster, breaks = breaks, plot = FALSE)

plot(h.prior, xlim = range(prior, poster, na.rm = TRUE), 
     ylim = c(0, max(h.prior$count, h.poster$count)), main = "", 
     xlab = "", col = pri.col, border = pri.col)
plot(h.poster, xlim = range(prior, poster, na.rm = TRUE), col = post.col, 
     border = post.col, add = TRUE)
abline(v = median(prior), col = "blue", lwd = 2)
abline(v = median(poster), col = "red", lwd = 2)
legend("topleft", legend = c("Prior", "Posterior"), lty = c(1,1),
       lwd = c(2,2), col = c("blue", "red"), bty = "n")
```
what does the relationship between yearly BP and ice look like (similar to 
what we did above for phiA)
```{r}
yearly.BP <- apply(post$BP,2,mean)
plot(yearly.BP ~ ice.data4.5[2:113])
```

\newpage
# correlation plots
```{r}
hold2 <- sample(c(1:40000), 1000, replace = FALSE)
```
First, looking at the correlation between different LH parameters, specifically phiA, phi0, F and BP. In each pair, first a figure is given to show an example of the relationship between the two parameters, then a histogram is given showing distribution of correlations between the parameters using 1,000 posterior draws from the 10,000 retained. In the histogram plot, the percent of the correlations that are significant (at p < 0.05) in EITHER direction is shown. 

## phiA and phi0
```{r}
plot(post$phiA[1,]~post$phi0[1,], main = "Relationship between phiA and phi0", bty = "l")
phiAphi0 <- rep(NA, length(hold2))
phiAphi0p <- rep(NA, length(hold2))
for (i in 1:length(hold2)){
  phiAphi0[i] <- cor.test(post$phiA[i,], post$phi0[i,])$estimate
  phiAphi0p[i] <- cor.test(post$phiA[i,], post$phi0[i,])$p.value
}
``` 

```{r}
hist(phiAphi0, main = "Correlation of phiA and phi0 estimates", xlab = "")
phiAphi0sign <- round(sum(phiAphi0p < 0.05)/length(hold2)*100,2) 
text(0.2, 150, labels = bquote("percent sign" ==.(phiAphi0sign)))
```

## phiA and F
```{r}
plot(post$phiA[1,]~post$F[1,], main = "Relationship between phiA and F", bty = "l")
phiAF <- rep(NA, length(hold2))
phiAFp <- rep(NA, length(hold2))
for (i in 1:length(hold2)){
  phiAF[i] <- cor.test(post$phiA[i,], post$F[i,])$estimate
  phiAFp[i] <- cor.test(post$phiA[i,], post$F[i,])$p.value
}

hist(phiAF, main = "Correlation of phiA and F estimates", xlab = "")
phiAFsign <- round(sum(phiAFp < 0.05)/length(hold2)*100,2) 
text(0.3, 125, labels = bquote("percent sign" ==.(phiAFsign)))
```


## phiA and BP
```{r}
plot(post$phiA[1,]~post$BP[1,], main = "Relationship between phiA and BP", bty = "l")
phiABP <- rep(NA, length(hold2))
phiABPp <- rep(NA, length(hold2))
for (i in 1:length(hold2)){
  phiABP[i] <- cor.test(post$phiA[i,], post$BP[i,])$estimate
  phiABPp[i] <- cor.test(post$phiA[i,], post$BP[i,])$p.value
}

hist(phiABP, main = "Correlation of phiA and BP estimates", xlab = "")
phiABPsign <- round(sum(phiABPp < 0.05)/length(hold2)*100,2) 
text(0.2, 150, labels = bquote("percent sign" ==.(phiABPsign)))
```

## phi0 and F
phi0 feeds into F

```{r}
plot(post$phi0[1,]~post$F[1,], main = "Relationship between phi0 and F", bty = "l")
phi0F <- rep(NA, length(hold2))
phi0Fp <- rep(NA, length(hold2))
for (i in 1:length(hold2)){
  phi0F[i] <- cor.test(post$phi0[i,], post$F[i,])$estimate
  phi0Fp[i] <- cor.test(post$phi0[i,], post$F[i,])$p.value
}

hist(phi0F, main = "Correlation of phi0 and F estimates", xlab = "")
phi0Fsign <- round(sum(phi0Fp < 0.05)/length(hold2)*100,2) 
text(0.8, 100, labels = bquote("percent sign" ==.(phi0Fsign)))
```

## phi0 and BP
```{r}
plot(post$phi0[1,]~post$BP[1,], main = "Relationship between phi0 and BP", bty = "l")
phi0BP <- rep(NA, length(hold2))
phi0BPp <- rep(NA, length(hold2))
for (i in 1:length(hold2)){
  phi0BP[i] <- cor.test(post$phi0[i,], post$BP[i,])$estimate
  phi0BPp[i] <- cor.test(post$phi0[i,], post$BP[i,])$p.value
}

hist(phi0BP, main = "Correlation of phi0 and BP estimates", xlab = "")
phi0BPsign <- round(sum(phi0BPp < 0.05)/length(hold2)*100,2) 
text(0.2, 100, labels = bquote("percent sign" ==.(phi0BPsign)))
```

## F and BP
BP feeds into F

```{r}
plot(post$F[1,]~post$BP[1,], main = "Relationship between F and BP", bty = "l")
FBP <- rep(NA, length(hold2))
FBPp <- rep(NA, length(hold2))
for (i in 1:length(hold2)){
  FBP[i] <- cor.test(post$F[i,], post$BP[i,])$estimate
  FBPp[i] <- cor.test(post$F[i,], post$BP[i,])$p.value
}

hist(FBP, main = "Correlation of F and BP estimates", xlab = "")
FBPsign <- round(sum(FBPp < 0.05)/length(hold2)*100,2) 
text(0.2, 200, labels = bquote("percent sign" ==.(FBPsign)))
```

\newpage
Lastly, looking at any correlations in the ice parameters between phiA, phi0, and F.
```{r}
dat <- data.frame(cbind(ice.phiA = post$beta[hold2,1],
                        ice2.phiA = post$beta[hold2,2],
                        ice.phi0 = post$beta[hold2,3],
                        ice2.phi0 = post$beta[hold2,4],
                        betaF.ice = post$betaF.ice[hold2],
                        betaF.ice2 = post$betaF.ice2[hold2]))
```

## ice effects
```{r}
chart.Correlation(dat[,], histogram=TRUE, pch=19)
```

